\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate Z-axis

\section{GDML to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 
solids can be mapped to a FLUKA \verb|REGION|. Some solids in Geant4 directly map to 
a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
A region is a region of space which is formed of bodies and the operators + (intersection), - 
(complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and, in general, infinite extent bodies have 
benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
plane (PLA), Z axis aligned cylinder (ZCC), Z axis aligned elliptical cylinder (ZEC), 
sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA). 
\begin{figure}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
\caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
the original model in \PYGEOMETRY{}, right panel: the converted FLUKA geometry 
viewed in FLAIR. The example is a sector bend dipole electromagnet.}
\label{fig:gdml-flair}
\end{center}
\end{figure}

>>>>

\section{GDML to FLUKA conversion}
It is relatively straight forward to convert Geant4 geometry to FLUKA. Each of the Geant4 
solids can be mapped to a FLUKA \verb|REGION|. Some solids in Geant4 directly map to 
a FLUKA body, others need a construction of a simple FLUKA CSG tree. Table~\ref{tab:geant2fluka}
lists the mapping between Geant4 solids and the bodies used to compose a FLUKA region.
A region is a region of space which is formed of bodies and the operators + (intersection), - 
(complement) and | (union), also parentheses to indicate the order of operations. FLUKA 
has 20 bodies, listed in Table~\ref{tab:Fluka2Geant4}  and, in general, infinite extent bodies have 
benefits over finite ones. Key for conversion are XY-, XZ-, YZ-Planes (XYP, XZP, YZP), arbitrary 
plane (PLA), Z-axis aligned cylinder (ZCC), Z-axis aligned elliptical cylinder (ZEC), 
sphere (SPH), truncated right-angle cone (TRC) and general quadric surface (QUA). 
\begin{figure}
\begin{center}
\includegraphics[width=0.9\columnwidth]{./model-scene/CuboidalChamber.pdf}
\caption{Example conversion of a simple GDML geometry to FLUKA, left panel:  
the original model in \PYGEOMETRY{}, right panel: the converted FLUKA geometry 
viewed in FLAIR. The example is a sector bend dipole electromagnet.}
\label{fig:gdml-flair}
\end{center}
\end{figure}
